
---
## title: "Explained spc4sts: Statistical Process Control for Stochastic Textured Surfaces in R"
```{r}

library(EBImage)
library(keras)
require(spc4sts)
require(tiff)
##Simulating STS images using SarGen()
set.seed(1)
fig1_1 <- sarGen(phi1=.6, phi2=.35, sigma=.01, m=250, n=250)
fig1_2 <- sarGen(phi1=.6, phi2=.35, sigma=.01, m=250, n=250) 

## Inducing Image with imposeDefect()
set.seed(3)
img2<- sarGen(phi1=.6, phi2=.35, sigma=.01, m=250, n=250)
set.seed(30)
img3<- imposeDefect(img2, loc=NULL, a=4, b=10, phi1=0, phi2=0, sigma=0.01)$img
## Here the loc=NULL hence the location of defect is random.
## I am not sure how to put 'loc' values into the code.

```
## To generate Image with Global change : 
## change the process parameters.
```{r}

fig3_1 <- sarGen(phi1=.6, phi2=.35, sigma=.01, m=250, n=250)
fig3_2 <- sarGen(phi1=.35, phi2=.6, sigma=.01, m=250, n=250)

```

#STS image modeled in a generic manner based on supervised learning
```{r}
set.seed(11)
model <- surfacemodel(img=fig1_1, nb=1, xval=5,keep.residuals=TRUE, stationary.test=TRUE)
model
```

## Monitoring has 3 main steps
## 1) Model (which is done) & Capture IN Control surface behavior
## 2) Establish control limits
## 3) compute the monitoring statistic using monitoringStat()

## Fitting Model

```{r}
set.seed(11)
model<-surfacemodel(img=fig1_1, nb=1, keep.residuals = TRUE, stationary.test = TRUE)
model
```

## simulate 20 new IC images and find climit object which
## contains all the information needed for local defect monitoring.
```{r}
set.seed(2)
imgs <- array(0, c(250, 250, 20))
for (j in 1:dim(imgs)[3]) {imgs[,,j]<-sarGen(phi1=.6, phi2=.35, sigma=.01, m=250, n=250)}
cl<- climit(imgs, fa.rate=0.05, model, type=1, stat='ad', w=5, nD=10)
cl
```

#simulate 10 image for local monitoring.
#Here 5 images are similar IC(like fig1_1) and 5 contains local defects
```{r}
set.seed(22)
imgs1 <- array(0, c(250, 250, 10))
for (j in 1:dim(imgs1)[3]) imgs1[ , , j] <- sarGen(phi1=.6, phi2=.35)
imgs1_ld <- imgs1
for (j in 6:10) imgs1_ld[ , , j]<-imposeDefect(imgs1[ , , j])$img
```


#compute monitoring stats
```{r}
ls1_ld <- vector('numeric', 10)
for (j in 1:10) ls1_ld[j] <- monitoringStat(img=imgs1_ld[ , , j], model=model, cl=cl)$localStat
```

#Plot control charts for local defect monitoring 
```{r}
par(mar=c(2.5, 2.5, 1,1), mgp=c(1.5, 0.5, 0))
plotcc(statsII = ls1_ld, CL=cl$localStat$control.limit, statsI = cl$localStat$PIstats)
```


#dignoseLD(): produces binary image that highlights regions with potential defects for the given image
```{r}
ls2<- monitoringStat(img=img3, model=model, cl=cl)
bimg<- diagnoseLD(ms=ls2, dth=cl$diagnostic.threshold)
```

#global change
## reuse the model fitted.In the second step, we reuse the set
## of 20 Phase I IC images imgs to establish the CL.

```{r}
cl2<- climit(imgs=imgs, fa.rate=.05, model=model, type=2)
cl2
```

## Monitoring Global change
## Reuse 5 Phase 2 IC images and generate 5 OC Phase 2 images 
## with global change by reducing their phi1 and phi2.

```{r}
set.seed(66)
imgs1_gc <- imgs1
for (j in 6:10) imgs1_gc[ , , j] <- sarGen(phi1 =0.6*0.99, phi2= 0.35*0.99)
ls1_gc <- vector('numeric', 10)
for (j in 1:10) ls1_gc[j] <- monitoringStat(img=imgs1_gc[ , , j], model=model, cl=cl2)$globalStat

```

#plotting global chaanges: 
```{r}
par(mar= c(2.5, 2.5, 1, 1), mgp= c(1.5, 0.5, 0))
plotcc(statsII = ls1_gc, CL=cl2$globalStat$control.limit.ecdf, statsI = cl2$globalStat$PIstats)

```

#Computing pairwise dissimilarity matrices of STS
#This matrices can be used for different ML tasks like clustering,
##Classification, outliner detection and manifold learning.
```{r}

imgs1_pd<-imgs1
imgs1_pd[ , ,10] <-fig3_2
print(disMat(imgs1_pd, nb=1, cp=1e-3, subsample= c(0.5, 0.25)), digits=2)$KL
```




